\section{\MakeUppercase{Feasibility Analysis}}
The feasibility analysis for the project includes technical feasibility, economic feasibility, legal feasibility, and time constraints feasibility as discussed below.
    \subsection{Technical Feasibility}
    The required technologies for video compression, such as H.264, H.265/\gls{hevc}, VP9, AV1, and various encoding and decoding algorithms, are widely available. The project utilizes a neural network-based approach for video compression, thus the availability of computing powers through NVIDIA GTX 1650, NVIDIA RTX 4090 and platforms like Google Colab allows for sufficient training and inference testing.
    \subsection{Economical Feasibility}
    For the dataset, we have utilized a free dataset. For the training computing resources, we have access to an RTX 4090 GPU from our supervisor, ensuring that our project is economically feasible. This setup significantly reduces our operational costs and enhances the viability of our project from a financial perspective.
    \subsection{Legal Feasibility}
    Legal feasibility considerations include the use of dataset Vimeo-90K for training neural network models. While these datasets are widely used in research, it is important to note that specific datasets may have copyright restrictions or usage terms that require compliance. Proper attribution and adherence to licensing terms are essential to ensure legal compliance and avoid copyright infringement issues.
    \subsection{Schedule Feasibility}
    Effective project management practices, including task prioritization, milestone tracking, and regular progress evaluations, are implemented to ensure timely completion of project objectives. The utilization of project management tools and techniques, along with efficient resource allocation, facilitates meeting project deadlines and achieving desired outcomes within the specified time frame. The overview of our project schedule can be seen on \autoref{fig:gantt-b}.
\pagebreak
